BayesComp 2023 and Bayesian Inference of Epidemics abstract submission

### 2022-10-06 docs/bayescomp.Rmd
Update BayesComp abstract based on feedback from Alex

```{r echo=FALSE}
title <- "Integrated nested Laplace approximations for extended latent Gaussian models, with application to the Naomi HIV model"
abstract <- "Naomi (Eaton et al, 2021) is a spatial evidence synthesis model used by countries in sub-Saharan Africa to produce district-level HIV epidemic indicators. We combine the simplified integrated nested Laplace approximation approach of Wood (2020) with adaptive Gaussian hermite quadrature to enable fast and accurate inference for Naomi and other extended latent Gaussian models. Using data from Malawi, we compare our inference method to both a simple Gaussian approximation via `TMB` and to NUTS via `tmbstan`. We provide an easy to use implementation as a part of the `aghq` R package allowing flexible use of the INLA method for a broader class of models than `R-INLA`. Given a `TMB` template, using our method requires minimal additional code."
```

>>>>

```{r echo=FALSE}
title <- "Integrated nested Laplace approximations for extended latent Gaussian models, with application to the Naomi HIV model"
abstract <- "Naomi (Eaton et al, 2021) is a spatial evidence synthesis model used to produce district-level HIV epidemic indicators in sub-Saharan Africa. Performing computationally intensive inference using simulation-based methods like MCMC is infeasible in this setting as the model must be able to be easily run in production by countries, using their own data. We propose a new inference method which combines the simplified integrated nested Laplace approximation approach of Wood (2020) with adaptive Gaussian hermite quadrature to enable fast and accurate inference for Naomi and other extended latent Gaussian models. Using data from Malawi, we show that our inference method obtains substantially more accurate inferences than the simple Gaussian approximation obtained via `TMB`, as compared with gold-standard NUTS results obtained via `tmbstan`. We provide an easy to use implementation as a part of the `aghq` R package allowing flexible use of the INLA method for a broader class of models than `R-INLA`. Given a `TMB` template, using our method requires minimal additional code."
```
